A Systematic Literature Review on Extensions to Role Based Access Control

### 2013-04-25 paper/sections/core_rbac.tex
Background - Adds edits for the background section.

NIST's work can directly benefit organizations by lowering cost of early phase R\&D and implementation costs of RBAC.
Since RBAC is introduced, 2010 RTI report showed that the the rate of RBAC adoption is rapidly growing for recent years. 
The analysts estimate that, by the end of 2010, at least a part of permission of systems use RBAC for more than 50\% of IT users at organizations, which
hire more than 500 employees. For economic estimate analysis, the analysts estimate that RBAC technology has generated \$6.1 billion in net economic benefits to industry, of which \$1.1 billion is attributable to NIST RBAC standard work.

The NIST RBAC model proposed by Ferraiolo et al. \cite{ferraiolo} and later adopted as the official standard for RBAC by the INCITS includes three types of RBAC models: core RBAC, hierarchal RBAC, and constrained RBAC.
Since the basis for our review is extensions to the core model, we describe the core model, associated entities and other terminology encountered across the space of our review. Then, we describe hierarchal RBAC and constrained RBAC, which are developed by incoporating new features into the core RBAC.

>>>>

NIST's work can directly benefit organizations by lowering cost of early phase R\&D and the implementation of RBAC.
Since the RBAC standard was first introduced, a 2010 report by RTI International showed that the the rate of RBAC adoption has rapidly grown over recent years \cite{o20102010}. 
The analysts estimate that, by the end of 2010, at least a part of permission of systems use RBAC for more than 50\% of IT users at organizations, which
hire more than 500 employees. For economic estimate analysis, the analysts estimate that RBAC technology has generated \$6.1 billion in net economic benefits to industry, of which \$1.1 billion is attributable to NIST RBAC standard work.

The NIST RBAC standard model proposed by Ferraiolo et al. \cite{ferraiolo} and later adopted as the official standard for RBAC by the INCITS includes three levels of RBAC: core RBAC, hierarchal RBAC, and constrained RBAC.
Since the basis for our review is extensions to the RBAC standard model, we describe the core model, associated entities and other terminology encountered across the space of our review. Then, we describe hierarchal RBAC and constrained RBAC, which are developed by incoporating new features into the core RBAC.
